The globular cluster system of the Auriga simulations

### 2020-04-14 response_to_referee.tex

\begin{document}

\section*{Introduction}
We thank the referee for a thoughtful and elaborate report. We address the 
comments in sections with headings that match those of the referee report, 
starting with the following listing of our response to the first 2 paragraphs in 
the introduction.
\begin{enumerate}
\item We updated the abstract and conclusion to clarify that we meant to describe
what would be needed for the environmental dependence of the formation and disruption
of bound clusters for the Auriga simulations to be consistent with the observations,
rather than to argue that the Auriga simulations reflect these trends.
\item
We feel that our conclusion would be too strongly phrased if we would generalise 
our results obtained using the Auriga simulations to cosmological simulations 
in general. We find that age-selected stellar particles in the Auriga simulations 
do not reproduce key properties of observed GC systems in the Milky Way and M31.
However, our results might reflect characteristics that are specific to Auriga, 
e.g. that the galaxy formation model overmixes metals at early times. 
Therefore we did add a final bulletpoint to our conclusion to clarify the above, 
but we limit the scope to the Auriga simulations. Thanks for pointing this out!

Furthermore, we clarified in the manuscript that we investigate the metallicity
and galactocentric radius because these properties are available for the observed
GC systems and in the simulations.
% \item TODO: disussion of implications for wider context.
\end{enumerate}

\section*{General comments about style}
\begin{itemize}
\item Numerical quantities are now described in arabic numbers instead of words.
\item We now first use the name of the physical quantities in the given example,
    followed by the symbolic representation.
\item The text has been updated to reduce the usage of parenthesis.
\item Colloquial expressions have been rephrased.
\item We replaced `Sec.' by `Section' to refer to sections in the present work.
Moreover, we changed `Sec.' to `section' to refer to a section in one of the references.
\item All acronyms are introduced the first time they appear in the text
(MW, M31, GC, GCS, YMC, ISM, SN, DM, and Au). The subset thereof that appears 
in the abstract is also introduced the first time it appears.
\item The colour palette has been updated to improve colourblind-friendliness.
\item We no longer use blue and red to prevent confusion because they are 
typically used for metal-poor and metal-rich populations.
\end{itemize}

@@

\subsection*{Sect. 4 -}
\begin{itemize}
\item We added the mean number of GC candidates compared to the mean number of
star particles in the Auriga L4 galaxies. In addition, Figure 3 now shows the 
number of star particles included in each subset.
\item We clarified at various places whether we mean the mean or median among
the simulations, or if we refer to the absolute value of one of the galaxies.
\item We added the suggestion in the 3rd paragraph of section 4.1.
\item Bimodality in GC systems is now discussed in the introduction.
\item Figure 4 - now has a vertical line to indicate the metallicity cut 
between metal-poor and metal-rich GC subpopulations in the Milky Way.
\item We added a sentence about the cluster formation efficiency model of 
Kruijssen (2012) in the last paragraph of section 4.1.
\item We now show the median instead of the mean for the galactocentric radius in
section 4.2 and Figure 6.
\item Figure 6: no changes were made for rescaling the galaxies (i.e. we still
use the virial radius)
\item Figure 5 and 7: shaded regions now show the 25-75th percentiles.
\item We added a brief discussion of Figure 8.
\item We clarified that we are referring to Figure 5 and Figure 7 for the claims about
the {\it in~situ} and accreted component in the third paragraph of section 4.3.
\item Figure 9: The values are removed from the masked upper right corner bins.
\item Figure 2,8,9: The values of the upper and right axes have been removed from
Figure 2 and 9 (observations) for clarity (rather than the suggestion to add 
axis labels and units). However, we did not mask these bins for Figure 8 (Auriga)
because it illustrates our finding that the simulations produce a considerable
amount of mass in GC candidates with low metallicities at large radii.
\end{itemize}

\subsection*{Sect. 5 -}
\begin{itemize}
\item We added references to Deason et al. (2015) and Conroy et al. (2019) in
the first paragraph of section 5.1.
\item We included a discussion of bimodality in metallicities in the introduction.
In addition to that, the results of Usher et al. (2012) ``imply that most early-type 
galaxies in the SLUGGS survey have bimodal metallicity as well as colour distributions'',
and ``Combined with previous studies, nine of 12 galaxies show evidence for bimodality
while in the remaining three galaxies bimodality cannot be ruled out.''. Our 
interpretation of this study seems to differ from that of the referee.
\item We still find that the accreted star particles are more metal-poor than 
those that have formed {\it in~situ} if we lower the age cut to 8 or 6 Gyr.
This has been added in section 5.3.
\item We removed the quoted sentence.
\item Our definition of `accreted GC candidate' considers when the GC candidate 
was accreted onto the main object, not when it was formed. The age cut does not
affect the time of accretion, but the time of accretion could have been before redshift
$z=2$ (which would be inconsistent with the definition of Kruijssen et al. 2019).
\item We clarified which which galaxy Brodie \& Strader provide the quoted number.
\item We clarified footnote 8.
of Kruijssen (2019) for {\it ex~situ} GC formation.
\end{itemize}

### 2020-05-13 AurigaGCS_20200414.tex
Ready for R2 (pending approval FG)

As for the formation timeline, the scenarios (and flavours thereof) of \citet{
1985ApJ...298...18F} and \citet{1992ApJ...384...50A} are intertwined because
accretion and mergers continuously occurs during the hierarchical build-up of
galaxies. Various (other) hierarchical formation channels thus combine different
aspects of the aforementioned paradigms, such as GC formation in (small) galactic
disks before they are accreted onto an assembling galaxy \citep[e.g.][]{
2000ApJ...533..869C, 2002ApJ...567..853C, 2002MNRAS.333..383B, 2003egcs.conf..224G}. 
We refer to \citet{2001astro.ph..8034G} for a scoreboard of GC formation models 
compared to observations of the MW GCSs.

An idea that has recently been studied extensively is the hypothesis that the formation
mechanisms of young massive clusters \citep[YMCs, see][for a review]{2010ARA&A..48..431P} 
and GCs are the same. The proximity of YMCs in the local Universe allows to study these 
processes with a level of detail that cannot be achieved for GCs at high redshifts. In 
this framework, differences between both classes of objects are caused by nearly a 
Hubble time of (dynamical) evolution \citep[e.g.][]{1987degc.book.....S}. This picture 
is based on observed similarities between YMCs and GCs
\citep[e.g.][]{1992AJ....103..691H,1999AJ....118.1551W} and strengthened by observations
of gravitationally lensed objects at high redshifts ($z = 2-6)$. These sources have 
properties reminiscent of (local) YMCs and may be GC progenitors at times of formation 
\citep{2017MNRAS.467.4304V,2017ApJ...843L..21J}. The modelling work by 
\citet{2011MNRAS.414.1339K,2012MNRAS.421.1927K,2015MNRAS.454.1658K} is now 
incorporated into cosmological zoom simulations and shows promising results
\citep{2018MNRAS.475.4309P,2019MNRAS.486.3134K}.

The (mass) resolution of cosmological zoom simulations has reached the mass range 
populated by GCs, and the gravitational force softening can be as low several 
parsec. A number of groups can thus incorporate formation of (globular) star 
clusters into their high-resolution hydrodynamical simulations. \citet{2016ApJ...831..204R} 
ran parsec scale simulations of the high-redshift universe 
prior to reionization (the simulations stop at $z=9$), \citet{2017ApJ...834...69L} 
implement a new subgrid model for star (cluster) formation and run simulations 
that reach $z=3.3$, and the run of \citet{2017MNRAS.465.3622R} reaches $z=0.5$. 
\citet{2018MNRAS.474.4232K} find that mergers can push gas to high density that
quickly forms clustered stars that end up tightly bound by the end of the 
simulation. A somewhat different approach couples semi-analytical models to DM-only
simulations \citep{2010ApJ...718.1266M,2014ApJ...796...10L,2018MNRAS.480.2343C,
2019MNRAS.486..331C,2019arXiv190505199C}, as is done in the work by 
\citet{2019MNRAS.482.4528E}.

In this work we use state of the art simulations that produce realistic spiral 
galaxies (MW analogues) at redshift zero for which several global properties 
are consistent with the observations. The question thus naturally arises whether 
the star formation histories of the simulations give rise to a GCS similar to 
the MW and/or Andromeda (M31) GCSs. In particular, 
we use the Auriga simulations \citep[][hereafter G17]{2017MNRAS.467..179G}, 
further described in Section~\ref{sec:auriga}. We investigate whether the star 
formation model implemented produces metallicity, radial, and metallicity-radial 
distributions that are consistent with the MW and/or M31 GCSs, and whether the 
model produces enough stellar mass with the right properties. Moreover, the simulations
provide us with the history of the star particles, which allows us to investigate
the differences between these properties for sub populations that have formed 
{\it in~situ} versus those that have been accreted. We focus on the metallicity
and radial distributions because observations of the red and blue GCs show
distinct differences between these properties.

The plan of the paper is as follows. We summarise the relevant characteristics 
of the Auriga simulations in section~\ref{sec:auriga}, followed by a summary of 
the observations of the MW and M31 GCSs
in section~\ref{sec:observations} that we use to compare our simulations to in
section~\ref{sec:results}. We discuss our findings in section~\ref{sec:discussion}
to come to our conclusions in section~\ref{sec:conclusions}.

% Referee: ``\citet{2012MNRAS.426.1475U} shows the great variety in GC metallicity distributions
% present in the sample of early-type galaxies of the SLUGGS survey contradicts
% the classical idea that all the metallicity distributions of GCs should be bimodal.''

\section{The Auriga simulations}
\label{sec:auriga}
We use the Auriga simulations \citepalias{2017MNRAS.467..179G}, a suite of 
high-resolution cosmological zoom simulations of MW analogues. The MW-mass
selected initial conditions in the range $1-2 \times 10^{12}$~M$_{\odot}$
were selected from the \mbox{\textsc{eagle}} DM only box, see 
\citetalias{2017MNRAS.467..179G} for details. The simulations are 
performed with the \textsc{arepo} code \citep{2010MNRAS.401..791S, 2016MNRAS.455.1134P} 
that solves the magnetohydrodynamical equations on a moving mesh.

The galaxy formation model includes primordial and metal-line cooling with 
self-shielding corrections. Reionization is completed at redshift $6$ by a
time-varying spatially uniform UV background \citep{2009ApJ...703.1416F, 
2013MNRAS.436.3031V}. The interstellar medium (ISM) is described by an equation of 
state for a two-phase medium in pressure equilibrium \citep{2003MNRAS.339..289S}: 
cold clouds embedded in a hot ambient medium, whose mass and energy densities
are described by processes important for star formation, such as the condensation 
of cold clouds and the photoevaporation of clouds. Stars form stocastically in 
thermally unstable gas with a density threshold of $n = 0.13 \, \text{cm}^{-3}$,
and consecutive stellar evolution is accounted for. The channel for energetic
stellar feedback is from non-local type II supernovae (SN), which is modelled 
with wind particles (\citealt{2014MNRAS.437.1750M}; \citetalias{2017MNRAS.467..179G}).
Galactic winds enrich the ISM with metals from SNIa, SNII, and asymptotic giant 
branch (AGB) stars \citep{2013MNRAS.436.3031V}. Supermassive
black holes grow via Bondi–Hoyle–Lyttleton accretion \citep{1944MNRAS.104..273B,
1952MNRAS.112..195B}, and feedback from the active galactic nuclei has a low-accretion
and high-accretion mode (radio and quasar) (\citealt{2005MNRAS.361..776S, 
2014MNRAS.437.1750M}; \citetalias{2017MNRAS.467..179G}). Finally, the simulations 
follow the evolution of a magnetic field of $10^{-14}$ (comoving)~G seeded at 
$z = 127$ \citep{2013MNRAS.432..176P, 2014ApJ...783L..20P}.

@@

The Auriga suite has a fiducial baryonic mass resolution $m_b$~=~$5 \times 10^4$~M\Sun,
with gravitational softening of collissionless particles $\epsilon$~=~369~pc.
Simulations at this resolution are referred to as level 4 (L4). Selected
initial condition runs are acompanied by the lower (higher) resolution level L5 (L3).
The resolution for these levels is $m_b$~=~$4 \times 10^5$~M\Sun \, with 
$\epsilon$~=~738~pc, and $m_b$~=~$6 \times 10^3$~M\Sun \, with $\epsilon$~=~184~pc,
respectively. The mass resolution of the Auriga simulations is thus close to the 
characteristic peak mass of the lognormal GC mass distribution of $10^{5}$~M\Sun 
\citep{1991ARA&A..29..543H}, although the gravitational softening is two orders 
of magnitudes larger than typical GC radii of several parsec. High-density gaseous 
regions are thus not expected to produce surviving stellar clumps with masses and 
radii consistent with GCs because such objects would numerically disperse, even 
in the highest-resolution runs. On the other hand, we can investigate (statistical) 
properties of age-selected GC candidates because each star particle represents a
single stellar population with a total mass that could be consistent with one GC. 
This means that their formation sites and that of a real-world GC may be consistent.

\section{Observational data}
\label{sec:observations}
We describe the observations of the MW GCS in Section~\ref{sec:milkyway},
and of the M31 GCS in Section~\ref{sec:andromeda}. We discuss the age-estimates
in Section~\ref{sec:age}, the distribution of galactocentric radius in 
Section~\ref{sec:Rgc}, and the total mass in 2D bins of metallicity-galactocentric
radius in Section~\ref{sec:observations_FeHRgc}. We focus on metallicity and
galactocentric radius because these data are available in the observations and
in the Auriga simulations.

\subsection{Milky Way}
\label{sec:milkyway}
\citet[][2010 edition; hereafter H96e10]{1996AJ....112.1487H} provides a
catalogue\footnote{See \url{https://www.physics.mcmaster.ca/Fac_Harris/mwgc.dat}}
of the MW GCS that contains properties of 157 GCs. 
The authors initially estimated the number of GCs in the MW GCS to be 180~$\pm$~10,
thus, their catalogue to be ${\sim}$85\% complete. However, an additional 59 GCs
are claimed to have been discovered by various authors. The total number of GCs
in the MW might add up to 216 with recent estimates now anticipating an additional 
$30$~GCs yet to be discovered \citep[e.g.][and references therein]{2018ApJ...863L..38R}.
We still use data from the Harris catalogue, but caution that it may (only) be
50-70\% complete. Specifically, the relevant data fields that we use from H96e10
are the metallicity [Fe/H], the Galactic distance components $X$, $Y$, and $Z$ (in
kpc)\footnote{In a Sun-centered coordinate system: $X$ points toward Galactic
center, $Y$ in direction of Galactic rotation, and $Z$ toward the North Galactic
Pole. We calculate the galactocentric radius $r_{\text{gal}}=\sqrt{(X-r_\odot)^2
+ Y^2 + Z^2}$, assuming the solar radius $r_\odot=8$~kpc.}, and absolute
magnitude in the V~band, $M_V$. We use the V~band magnitude to calculate 
mass-estimates by assuming $M_{V,\odot}=4.83$ and a mass to light ratio 
$M/L_V = 1.7$~M$_{\odot}$/L$_{\odot}$, the mean for MW clusters \citep{2005ApJS..161..304M}. 
We supplement the catalogue with age-estimates from isochrone fits to stars near 
the main-sequence turnoff in 55 GCs \citep[][hereafter V13]{2013ApJ...775..134V}.

@@

\subsection{Andromeda}
\label{sec:andromeda}
\citet[][hereafter C11]{2011AJ....141...61C} and \citet[][hereafter CR16]{2016ApJ...824...42C}
present a uniform set of spectroscopic observations of the inner 
$1.6^\circ~({\sim}21)$~kpc of M31 that is believed to be 94\% complete. In addition,
the outer stellar halo of M31 up to $r_{\text{proj}}\sim150$~kpc is observed in 
the Pan-Andromeda Archaeological Survey \citep[PAndAS, ][hereafter H14]{2014MNRAS.442.2165H,
2014MNRAS.442.2929V, 2019MNRAS.484.1756M}. In fact, 
the work of H14 is incorporated in the latest public release\footnote{Last 
revised 23 Sep 2015, see \url{https://www.cfa.harvard.edu/oir/eg/m31clusters/M31_Hectospec.html}}
of the C11 and CR16 data sets. Therefore we use the latest data set of CR16 
because it is the most recent aggregated dataset of M31's GCS that contains GCs 
in the inner region and in the outer halo. The relevant fields in the CR16 dataset 
that we use are the age, metallicity, and the mass-estimate\footnote{The authors 
assumed $M/L_V = 2$ independent of [Fe/H]}. We calculate the galactocentric radii 
from the observed positions RA and DEC, further discussed in Sec.~\ref{sec:Rgc}.

\subsection{Age-estimates}
\label{sec:age}
The top panel of Figure~\ref{fig:MW-M31-age-Rgc} shows a histogram of the age-estimates
of the $55$ MW GCs in V13 and $88$ GCs in M31 for which age-estimates are available
in CR16. The mean age of the MW GCs in this data set is $11.9$~Gyr and the 
standard deviation is $0.8$~Gyr. Furthermore, only 1 of the 55 GC age-estimates is
below $10$~Gyr. The M31 GCS has a mean age of $11.0$~Gyr with a standard deviation 
of $2.2$~Gyr, and $24$ GCs have age-estimates below $10$~Gyr with a minimum age 
of $4.8$~Gyr. Based on these data, we find that the age distributions of the MW 
and M31 GCSs are not statistically consistent. Moreover, the MW appears 
to host a GCS that is somewhat older than that of M31.
This is somewhat surprising given that M31 is generally considered to be earlier
type than the MW meaning that an older stellar population would be naively expected.
However, we do caution that both data sets are incomplete and the age 
measurements have large uncertainties (of $1-2$~Gyr). On the other hand, the 
magnitude of the uncertainty is insufficient to explain the low-age tail in M31.

\subsection{Radial distribution}
\label{sec:Rgc}
The bottom panel of Figure~\ref{fig:MW-M31-age-Rgc} shows the radial distribution
of the MW and M31 GCS. We divide the radii of M31 by its virial radius\footnote{
$r_{\text{vir}}$ is the radius in a spherical `top-hat' perturbation model at which
the average density reaches an overdensity of $\Delta_{\text{vir}}=357$ times the 
background density} $r_{\text{vir,M31}} = 299$~kpc and multiply by 
$r_{\text{vir,MW}} = 261$~kpc to account for the different intrinsic sizes of both 
galaxies, adopting the values and cosmology from \citet{2017MNRAS.464.3825P}.
Values for $r_{\text{gal}}$ are readily available in H96e10 (assuming $r_{\odot}=8.0$~kpc), 
but the galactocentric radius of GCs in M31 is not available in CR16. Therefore, we 
follow \citet[][section~4.1]{2019arXiv190111229W} 
to calculate the projected radius $r_{\text{proj}}$ from the observed positions,
adopting M31's central position from the NASA Extragalactic 
Database\footnote{\url{https://ned.ipac.caltech.edu/}} $(\alpha_0, \, \delta_0) =
(0^{\text{h}}42^{\text{m}}44.35^{\text{s}}, \, +41^{\circ}16'08.63")$
and distance $D_{\text{M31}} = 780$~kpc \citep{2005MNRAS.356..979M,2012ApJ...758...11C}.
We calculate $r_{\text{gal}}$ as `average deprojected distance`
$r_{\text{gal}} = r_{\text{proj}} \times (4/\pi)$.

The solid lines show the distributions using all available data (because the
sky coordinates are known for each GC), while the subset for which age-estimates
are available is indicated using dotted lines. The latter shows a narrower range
of radii than the full data set: it appears that few age-estimates are available 
for the innermost ($<1$~kpc) GCs, and none for those beyond roughly $20$~kpc
(the halo GCs). We compare both distributions of the full data set (solid 
lines) and find that the MW has more GCs in the range $1-4$~kpc than M31
when accounting for the larger number of total GCs in M31. Interestingly, both
distributions show a similar trend for $r_{\text{gal}} > 4$~kpc and host a 
subpopulation of halo GCs. Our naive expectation would be that the spiral galaxies
in the Local Group host similar GC systems. However, the radial distributions of
the GCS of the MW and M31 are not statistically consistent with being drawn from 
the same underlying distribution due to substantial differences at intermediate radii.

@@

\subsection{Total GC mass in metallicity-radial space} 
\label{sec:observations_FeHRgc}
We show the two-dimensional mass-weighted metallicity-radial distribution of the
MW and the M31 GCS in the top and bottom panel of Figure~\ref{fig:observations_FeHRgc},
respectively. Note that the number of GCs is different than in 
Figure~\ref{fig:MW-M31-age-Rgc} because here we plot [Fe/H] between -2.5 and 0 
and $r_{\text{gal}}$ between 1 and 250 kpc whereas Figure~\ref{fig:MW-M31-age-Rgc}
shows the full range of metallicities and radii.

>>>>

As for the formation timeline, the scenarios (and flavours thereof) of \citet{
1985ApJ...298...18F} and \citet{1992ApJ...384...50A} are intertwined because
accretion and mergers continually occur during the hierarchical build-up of
galaxies. Various (other) hierarchical formation channels thus combine different
aspects of the aforementioned paradigms, such as GC formation in (small) galactic
disks before they are accreted onto an assembling galaxy \citep[e.g.][]{
2000ApJ...533..869C, 2002ApJ...567..853C, 2002MNRAS.333..383B, 2003egcs.conf..224G}. 
We refer to \citet{2001astro.ph..8034G} for a scoreboard of GC formation models 
compared to observations of the MW GCSs.

An idea that has recently been studied extensively is the hypothesis that the formation
mechanisms of young massive clusters \citep[YMCs, see][for a review]{2010ARA&A..48..431P} 
and GCs are the same. The proximity of YMCs in the local Universe allows to study these 
processes with a level of detail that cannot be achieved for GCs at high redshifts. In 
this framework, differences between the two classes of objects are caused by nearly a 
Hubble time of (dynamical) evolution \citep[e.g.][]{1987degc.book.....S}. This picture 
is based on observed similarities between YMCs and GCs
\citep[e.g.][]{1992AJ....103..691H,1999AJ....118.1551W} and strengthened by observations
of gravitationally lensed objects at high redshifts ($z = 2-6)$. These sources have 
properties reminiscent of (local) YMCs and may be GC progenitors at times of formation 
\citep{2017MNRAS.467.4304V,2017ApJ...843L..21J}. The modelling work by 
\citet{2011MNRAS.414.1339K,2012MNRAS.421.1927K,2015MNRAS.454.1658K} is now 
incorporated into cosmological zoom simulations and shows promising results
\citep{2018MNRAS.475.4309P,2019MNRAS.486.3134K}.

The (mass) resolution of cosmological zoom simulations has reached the mass range 
populated by GCs, and the gravitational force softening can be as low several 
parsec. A number of groups can thus incorporate formation of (globular) star 
clusters into their high-resolution hydrodynamical simulations. \citet{2016ApJ...831..204R} 
ran parsec scale simulations of the high-redshift universe 
prior to reionization (the simulations stop at $z=9$), \citet{2017ApJ...834...69L} 
implement a new subgrid model for star (cluster) formation and run simulations 
that reach $z=3.3$, and the run of \citet{2017MNRAS.465.3622R} reaches $z=0.5$. 
\citet{2018MNRAS.474.4232K} find that mergers can push gas to high density that
quickly forms clustered stars that end up tightly bound by the end of the 
simulation. A somewhat different approach couples semi-analytical models to DM-only
simulations \citep{2010ApJ...718.1266M,2014ApJ...796...10L,2018MNRAS.480.2343C,
2019MNRAS.486..331C,2019arXiv190505199C}, also done in the work by 
\citet{2019MNRAS.482.4528E}.

In this work we use state of the art simulations that produce realistic spiral 
galaxies (MW analogues) at redshift zero for which several global properties 
are consistent with the observations. The question thus naturally arises whether 
the star formation histories of the simulations could give rise to a GCS similar to 
the MW and/or Andromeda (M31) GCSs. In particular, 
we use the Auriga simulations \citep[][hereafter G17]{2017MNRAS.467..179G}, 
further described in Section~\ref{sec:auriga}. We investigate whether the star 
formation model implemented produces metallicity, radial, and metallicity-radial 
distributions that are consistent with the MW and/or M31 GCSs, and whether the 
model produces enough stellar mass with the right properties. Moreover, the simulations
provide us with the history of the star particles, which allows us to investigate
the differences between these properties for sub-populations that have formed 
{\it in~situ} versus those that have been accreted. We focus on the metallicity
and radial distributions because observations of the red and blue GCs show
distinct differences between these properties.

The plan of the paper is as follows. We summarise the relevant characteristics 
of the Auriga simulations in Section~\ref{sec:auriga}, followed by a summary of 
the observations of the MW and M31 GCSs
in Section~\ref{sec:observations} that we compare our simulations to in
Section~\ref{sec:results}. We discuss our findings in Section~\ref{sec:discussion}
to come to our conclusions in Section~\ref{sec:conclusions}.

\section{The Auriga simulations}
\label{sec:auriga}
We use the Auriga simulations \citepalias{2017MNRAS.467..179G}, a suite of 
high-resolution cosmological zoom simulations of MW analogues. The MW-mass
selected initial conditions in the range $1-2 \times 10^{12}$~M$_{\odot}$
were selected from the \mbox{\textsc{eagle}} DM-only box, see 
\citetalias{2017MNRAS.467..179G} for details. The simulations are 
performed with the \textsc{arepo} code \citep{2010MNRAS.401..791S, 2016MNRAS.455.1134P} 
that solves the magnetohydrodynamical equations on a moving mesh.

The galaxy formation model includes primordial and metal-line cooling with 
self-shielding corrections. Reionization is completed at redshift $6$ by a
time-varying spatially uniform UV background \citep{2009ApJ...703.1416F, 
2013MNRAS.436.3031V}. The interstellar medium (ISM) is described by an equation of 
state for a two-phase medium in pressure equilibrium \citep{2003MNRAS.339..289S}: 
cold clouds embedded in a hot ambient medium, whose mass and energy densities
are described by processes important for star formation, such as the condensation 
of cold clouds and the photoevaporation of clouds. Stars form stochastically in 
thermally unstable gas with a density threshold of $n = 0.13 \, \text{cm}^{-3}$,
and consecutive stellar evolution is accounted for. The channel for energetic
stellar feedback is from non-local type II supernovae (SN), which is modelled 
with wind particles (\citealt{2014MNRAS.437.1750M}; \citetalias{2017MNRAS.467..179G}).
Galactic winds enrich the ISM with metals from SNIa, SNII, and asymptotic giant 
branch stars \citep{2013MNRAS.436.3031V}. Supermassive
black holes grow via Bondi–Hoyle–Lyttleton accretion \citep{1944MNRAS.104..273B,
1952MNRAS.112..195B}, and feedback from the active galactic nuclei has a low-accretion
and high-accretion mode (radio and quasar) (\citealt{2005MNRAS.361..776S, 
2014MNRAS.437.1750M}; \citetalias{2017MNRAS.467..179G}). Finally, the simulations 
follow the evolution of a magnetic field of $10^{-14}$ (comoving)~G seeded at 
$z = 127$ \citep{2013MNRAS.432..176P, 2014ApJ...783L..20P}.

@@

The Auriga suite has a fiducial baryonic mass resolution $m_b$~=~$5 \times 10^4$~M\Sun,
with gravitational softening of collisionless particles $\epsilon$~=~369~pc.
Simulations at this resolution are referred to as level 4 (L4). Selected
initial condition runs are acompanied by the lower (higher) resolution level L5 (L3).
The resolution for these levels is $m_b$~=~$4 \times 10^5$~M\Sun \, with 
$\epsilon$~=~738~pc, and $m_b$~=~$6 \times 10^3$~M\Sun \, with $\epsilon$~=~184~pc,
respectively. The mass resolution of the Auriga simulations is thus close $10^{5}$~M\Sun,
to the characteristic peak mass of the lognormal GC mass distribution 
\citep{1991ARA&A..29..543H}, although the gravitational softening is two orders 
of magnitudes larger than typical GC radii of several parsec. High-density gaseous 
regions are thus not expected to produce surviving stellar clumps with masses and 
radii consistent with GCs because such objects would numerically disperse, even 
in the highest-resolution runs. On the other hand, we can investigate (statistical) 
properties of age-selected GC candidates because each star particle represents a
single stellar population with a total mass that could be consistent with one GC. 
This means that their formation sites could be consistent with those of real-world GCs.

\section{Observational data}
\label{sec:observations}
We describe observations of the MW GCS in Section~\ref{sec:milkyway} for these clusters,
and of the M31 GCS in Section~\ref{sec:andromeda}. We discuss age-estimates
in Section~\ref{sec:age}, their distribution of galactocentric radius in 
Section~\ref{sec:Rgc}, and their total mass in 2D bins of metallicity-galactocentric
radius in Section~\ref{sec:observations_FeHRgc}. We focus on both metallicity and
galactocentric radius because these data are available in the observations and
in the Auriga simulations.

\subsection{Milky Way}
\label{sec:milkyway}
\citet[][2010 edition; hereafter H96e10]{1996AJ....112.1487H} provides a
catalogue\footnote{See \url{https://www.physics.mcmaster.ca/Fac_Harris/mwgc.dat}}
of the MW GCS that contains properties of 157 GCs. 
The authors initially estimated the number of GCs in the MW GCS to be 180~$\pm$~10,
thus, their catalogue to be ${\sim}$85\% complete. However, an additional 59 GC
candidates have been discovered more recently by various authors. The total number of GCs
in the MW might thus be 216 with recent estimates now anticipating an additional 
$30$~GCs yet to be discovered \citep[e.g.][and references therein]{2018ApJ...863L..38R}.
We still use data from the Harris catalogue, but caution that it may (only) be
50-70\% complete. Specifically, the relevant data fields that we use from H96e10
are the metallicity [Fe/H], the Galactic distance components $X$, $Y$, and $Z$ (in
kpc)\footnote{In a Sun-centered coordinate system: $X$ points toward Galactic
center, $Y$ in direction of Galactic rotation, and $Z$ toward the North Galactic
Pole. We calculate the galactocentric radius $r_{\text{gal}}=\sqrt{(X-r_\odot)^2
+ Y^2 + Z^2}$, assuming the solar radius $r_\odot=8$~kpc.}, and absolute
magnitude in the V~band, $M_V$. We use the V~band magnitude to calculate 
mass-estimates by assuming $M_{V,\odot}=4.83$ and a mass to light ratio 
$M/L_V = 1.7$~M$_{\odot}$/L$_{\odot}$, the mean for MW clusters \citep{2005ApJS..161..304M}. 
We supplement the catalogue with age-estimates from isochrone fits to stars near 
the main-sequence turnoff in 55 GCs \citep[][hereafter V13]{2013ApJ...775..134V}.

@@

\subsection{Andromeda}
\label{sec:andromeda}
\citet[][hereafter C11]{2011AJ....141...61C} and \citet[][hereafter CR16]{2016ApJ...824...42C}
present a uniform set of spectroscopic observations of the inner 
$1.6^\circ~({\sim}21)$~kpc of M31 that is believed to be 94\% complete. In addition,
the outer stellar halo of M31 up to $r_{\text{proj}}\sim150$~kpc is observed in 
the Pan-Andromeda Archaeological Survey \citep[PAndAS, ][hereafter H14]{2014MNRAS.442.2165H,
2014MNRAS.442.2929V, 2019MNRAS.484.1756M}. In fact, 
the work of H14 is incorporated in the latest public release\footnote{Last 
revised 23 Sep 2015, see \url{https://www.cfa.harvard.edu/oir/eg/m31clusters/M31_Hectospec.html}}
of the C11 and CR16 data sets. Therefore we use the latest data set of CR16 
because it is the most recent aggregated dataset of M31's GCS that contains GCs 
in the inner region and in the outer halo. The relevant fields in the CR16 dataset 
that we use are the age, metallicity, and the mass-estimate\footnote{The authors 
assumed $M/L_V = 2$ independent of [Fe/H]}. We calculate the galactocentric radii 
from the observed positions RA and DEC, as further discussed in Section~\ref{sec:Rgc}.

\subsection{Age-estimates}
\label{sec:age}
The top panel of Figure~\ref{fig:MW-M31-age-Rgc} shows a histogram of the age-estimates
of the $55$ MW GCs in V13 and $88$ GCs in M31 for which age-estimates are available
in CR16. The mean age of the MW GCs in this data set is $11.9$~Gyr and the 
standard deviation is $0.8$~Gyr. Furthermore, only 1 of the 55 GC age-estimates is
below $10$~Gyr. The M31 GCS has a mean age of $11.0$~Gyr with a standard deviation 
of $2.2$~Gyr, and $24$ GCs have age-estimates below $10$~Gyr with a minimum age 
of $4.8$~Gyr. Based on these data, we find that the age distributions of the MW 
and M31 GCSs are not statistically consistent. The MW appears 
to host a GCS that is somewhat older than that of M31.
This is somewhat surprising given that M31 is generally considered to be earlier
type than the MW so that an older stellar population would naively be expected.
However, we do caution that both data sets are incomplete and the age 
measurements have large uncertainties (of $1-2$~Gyr). On the other hand, the 
magnitude of the uncertainty is insufficient to explain the low-age tail in M31.

\subsection{Radial distribution}
\label{sec:Rgc}
The bottom panel of Figure~\ref{fig:MW-M31-age-Rgc} shows the radial distribution
of the MW and M31 GCS. We divide the radii of M31 by its virial radius\footnote{
$r_{\text{vir}}$ is the radius in a spherical `top-hat' perturbation model at which
the average density reaches an overdensity of $\Delta_{\text{vir}}=357$ times the 
background density} $r_{\text{vir,M31}} = 299$~kpc and multiply by 
$r_{\text{vir,MW}} = 261$~kpc to account for the different intrinsic sizes of the two
galaxies, adopting the values and cosmology from \citet{2017MNRAS.464.3825P}.
Values for $r_{\text{gal}}$ are readily available in H96e10 (assuming $r_{\odot}=8.0$~kpc), 
but the galactocentric radius of GCs in M31 is not available in CR16. Therefore, we 
follow \citet[][section~4.1]{2019arXiv190111229W} 
to calculate the projected radius $r_{\text{proj}}$ from the observed positions,
adopting M31's central position from the NASA Extragalactic 
Database\footnote{\url{https://ned.ipac.caltech.edu/}} $(\alpha_0, \, \delta_0) =
(0^{\text{h}}42^{\text{m}}44.35^{\text{s}}, \, +41^{\circ}16'08.63")$
and the distance $D_{\text{M31}} = 780$~kpc \citep{2005MNRAS.356..979M,2012ApJ...758...11C}.
We estimate $r_{\text{gal}}$ as `average deprojected distance`
$r_{\text{gal}} = r_{\text{proj}} \times (4/\pi)$.

The solid lines show the distributions using all available data (because the
sky coordinates are known for each GC), while the subset for which age-estimates
are available is indicated using dotted lines. The latter shows a narrower range
of radii than the full data set: it appears that few age-estimates are available 
for the innermost ($<1$~kpc) GCs, and none for those beyond roughly $20$~kpc
(the halo GCs). We compare the two distributions of the full data set (solid 
lines) and find that the MW has more GCs in the range $1-4$~kpc than M31
when accounting for the larger number of total GCs in M31. Interestingly, the two 
distributions show a similar trend for $r_{\text{gal}} > 4$~kpc and host a 
subpopulation of halo GCs. Our naive expectation would be that the spiral galaxies
in the Local Group host similar GC systems. However, based on a two-sample KS test
we find that the radial distributions of the GCS of the MW and M31 are not statistically 
consistent with being drawn from the same underlying distribution due to substantial 
differences at intermediate radii.

@@

\subsection{Total GC mass in metallicity-radial space} 
\label{sec:observations_FeHRgc}
We show the two-dimensional mass-weighted metallicity-radius distribution of the
MW and the M31 GCS in the top and bottom panel of Figure~\ref{fig:observations_FeHRgc},
respectively. Note that the number of GCs is different than in 
Figure~\ref{fig:MW-M31-age-Rgc} because here we plot [Fe/H] between -2.5 and 0 
and $r_{\text{gal}}$ between 1 and 250 kpc whereas Figure~\ref{fig:MW-M31-age-Rgc}
shows the full range of metallicities and radii.
